Verifying Demonstrations

### 2018-05-30 paper/RelatedWork.tex
le monde for marches

Trusted infrastructure, for example deployed by a collection of  media outlets ~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability or privacy guarantees.

>>>>

Trusted infrastructure, for example deployed by a collection of  media outlets to count protesters passing a point on marches~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability or privacy guarantees.
